FEM Model Analysis

### 2021-05-05 FEM_R/model_analysis_core.Rmd
Added lots of new vars to roc_validation.do, fixed some errors, and added educ levels to output subgroups for analysis

smok.plot <-ggplot(data = smok.combined, aes(x = age, y = value)) +
                geom_bar(aes(fill = source), stat = "identity", position = "dodge") +
                labs(title = 'Comparison of smoking prevalence in the elderly in 2018', x = ' ', y = 'Prevalence (%)')

>>>>

smok.plot <-ggplot(data = smok.combined, aes(x = age, y = value)) +
                geom_bar(aes(fill = source), stat = "identity", position = "dodge") +
                labs(title = 'Prevalence of Smoking (2018)', x = ' ', y = 'Prevalence (%)')
